%\documentclass[toc]{Template/PoS}
\documentclass{Template/PoS}

\usepackage{enumitem}
\setlist{nolistsep}

\title{Integrating Network-Awareness and Network-Management into PhEDEx}

\ShortTitle{Network-Management in PhEDEx}

\author{\speaker{Vlad L\v{a}p\v{a}d\v{a}tescu}\\
Caltech / USA\\
E-mail: \email{vlad@cern.ch}}

\author{Tony Wildish\\
Princeton / USA\\
E-mail: \email{awildish@princeton.edu}}

\abstract{
PhEDEx is the data placement and management tool for the CMS experiment at the LHC. It controls the large-scale data-flows on the WAN across the experiment, typically handling 1 PB of data per week.
While robust, its architecture is now ten years old and has yet to fully
adapt to today's production environment, an environment in which the network is 
the fastest and most reliable component.

The ANSE (Advanced Network Services for Experiments) project, in the context of 
CMS, aims to greatly improve PhEDEx' network awareness for smart source 
selection, as well as to integrate bandwidth provisioning capabilities in the data 
transfer management. Both parts require a good knowledge of the network status, 
topology and of course, access to useful and up-to-date performance metrics.

One of the first steps towards this goal involved the identification of a mechanism 
for informing PhEDEx about independent network performance metrics. Methods 
for providing these metrics have been prototyped and verified in a LAN testbed 
using fake data transfer requests. This mechanism is already directly usable by CMS 
in their production environment.

Currently, the ANSE-PhEDEx testbed is spread over many servers at a number of 
sites. It is composed of several machines dedicated to PhEDEx site agents, one 
server holding the PhEDEx central agents, a central database and one server which 
contains the PhEDEx website and data-service. Some of the site nodes have 
additional attached storage nodes.

In this paper, we present the work that has been done in ANSE for PhEDEx.
This includes performance measurements using
the Fast Data Transfer (FDT) tool and the extension of the PhEDEx agent that downloads files to a site
to allow it to control the network via creation and use of dynamic circuits. We
present the results of our tests using these new features, on high-speed 
WAN circuits ranging from a few Gbps to 40Gbps and detail the development 
done within PhEDEx itself.

Finally, the paper will also describe the future plans for the project.}

\FullConference{International Symposium on Grids and Clouds (ISGC) 2014,\\
		23-28 March 2014\\
		Academia Sinica, Taipei, Taiwan}

\parindent=0pt 

\begin{document}


%TODO% 
%- Create subsection explaining why the average rates in PhEDEx are lower than average job transfer rates.
    %This is written in  ''Integration at the FileDownload Level'' but is common to ''Integration at the transfer-level''  

    
%- Tidy up section numbering 

    
\input{section-1-Introduction.tex}
\input{section-2-ANSE-setup.tex}
\input{section-3-Integrating-external-sources-of-information.tex}
\input{section-4-Integrating-virtual-circuts-into-PhEDEx.tex}
\input{section-5-Integration-at-the-transfer-level.tex}
\input{section-6-Integration-at-the-FileDownload-Level.tex}
\input{section-9-Summary.tex}
\input{bibliography.tex}

\end{document}